---
title: "ggplot 1"
author: "Julia Thompson"
date: "9/26/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggridges)
```

## Create the weather data

```{r load_data, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2017-01-01",
                      date_max = "2017-12-31") %>%
  mutate(
    name = dplyr::recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
ggplot(weather_df, aes(x=tmin, y=tmax)) + 
  geom_point()
```

Alternate way of making the same plot

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

Saving initial plots

```{r}
scatterplot = 
  weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()

scatterplot
```

Adding color

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4) + 
  geom_smooth(se = FALSE)
```


```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax, color = name)) + 
  geom_point(aes(color = name), alpha = .4) + 
  geom_smooth(se = FALSE) + 
  facet_grid(~name)
```

New plot

```{r}
weather_df %>%
  ggplot(aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = .5) + 
  geom_smooth(se = FALSE)
```

Learning assessment

```{r}
weather_df %>% 
  filter(name == "CentralPark_NY") %>% 
  mutate(tmax_fahr = tmax * (9 / 5) + 32,
         tmin_fahr = tmin * (9 / 5) + 32) %>% 
  ggplot(aes(x = tmin_fahr, y = tmax_fahr)) +
  geom_point(alpha = .5) + 
  geom_smooth(method = "lm", se = FALSE)
```

2D density

```{r}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_bin2d() #instal hexbin to use geom_hex()
```

## Even more plots

Univariate plots -- understanding one variable!

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + 
  geom_histogram(position = "dodge")
```

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + 
  geom_histogram() + 
  facet_grid(~name)
```

Density plot

```{r}
weather_df %>%
  ggplot(aes(x = tmax, fill = name)) + 
  geom_density(alpha = .3) 
```

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_boxplot()
```

Violin plots. These could be useful when you have a lot of groups and you want to check for bimodality etc. but otherwise not that great.

```{r}
weather_df %>%
  ggplot(aes(x = name, y = tmax)) +
  geom_violin()
```

Ridge plots - useful when you have lots of groups

```{r}
weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```

## Saving a plot

Note: you can save by clicking export on the right plot panel, but this is not reproducable so don't do it. Write it in your code!

```{r}
ggp_ridge_temp = 
  weather_df %>%
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()

ggsave("ggplot_temp_ridge.pdf", ggp_ridge_temp)
```

```{r, fig.width=6}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4) + 
  geom_smooth(se = FALSE)
```

```{r, fig.width=12}
weather_df %>%
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = .4) + 
  geom_smooth(se = FALSE)
```
